\documentclass[handout, xcolor=svgnames]{beamer}\usetheme{Montpellier}\usecolortheme{dolphin}\usepackage{pgfpages}\pgfpageslogicalpageoptions{1}{border code=\pgfusepath{stroke}}\pgfpageslogicalpageoptions{2}{border code=\pgfusepath{stroke}}\pgfpageslogicalpageoptions{3}{border code=\pgfusepath{stroke}}\pgfpageslogicalpageoptions{4}{border code=\pgfusepath{stroke}}\author{Dillon De Silva}\mode<handout> {\usepackage{pgfpages}\pgfpagesuselayout{6 on 1}[a4paper]}\begin{document}\begin{frame}\begin{center}\Huge Dylan Tazawa-Lim  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Vincent Crisostomo  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Elisa Liminto  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Kayla McGregor  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Geetanjali Gupta  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Tanishkaa Ramesh  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Vincent Crisostomo,  \\Welcome to SYNCS Camp! Your target is \color{red} Elisa Liminto\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Dylan Tazawa-Lim,  \\Welcome to SYNCS Camp! Your target is \color{red} Vincent Crisostomo\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Kayla McGregor,  \\Welcome to SYNCS Camp! Your target is \color{red} Geetanjali Gupta\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Elisa Liminto,  \\Welcome to SYNCS Camp! Your target is \color{red} Kayla McGregor\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Tanishkaa Ramesh,  \\Welcome to SYNCS Camp! Your target is \color{red} Emily Zhou\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Geetanjali Gupta,  \\Welcome to SYNCS Camp! Your target is \color{red} Tanishkaa Ramesh\end{center}\end{frame}\begin{frame}\begin{center}\Huge Emily Zhou  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Jeffrey Liang  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Ruchit Karnik  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Manasvi Singh  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Ishika Yadav  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Cynthia Zhu  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Jeffrey Liang,  \\Welcome to SYNCS Camp! Your target is \color{red} Ruchit Karnik\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Emily Zhou,  \\Welcome to SYNCS Camp! Your target is \color{red} Jeffrey Liang\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Manasvi Singh,  \\Welcome to SYNCS Camp! Your target is \color{red} Ishika Yadav\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Ruchit Karnik,  \\Welcome to SYNCS Camp! Your target is \color{red} Manasvi Singh\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Cynthia Zhu,  \\Welcome to SYNCS Camp! Your target is \color{red} Agrimaa Singh\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Ishika Yadav,  \\Welcome to SYNCS Camp! Your target is \color{red} Cynthia Zhu\end{center}\end{frame}\begin{frame}\begin{center}\Huge Agrimaa Singh  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Sangam Shakya  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Majed Al Ali  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Tiya Agrawal  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Damien Chim  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Bryan Sihotang  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Sangam Shakya,  \\Welcome to SYNCS Camp! Your target is \color{red} Majed Al Ali\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Agrimaa Singh,  \\Welcome to SYNCS Camp! Your target is \color{red} Sangam Shakya\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Tiya Agrawal,  \\Welcome to SYNCS Camp! Your target is \color{red} Damien Chim\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Majed Al Ali,  \\Welcome to SYNCS Camp! Your target is \color{red} Tiya Agrawal\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Bryan Sihotang,  \\Welcome to SYNCS Camp! Your target is \color{red} Stephanie Dam\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Damien Chim,  \\Welcome to SYNCS Camp! Your target is \color{red} Bryan Sihotang\end{center}\end{frame}\begin{frame}\begin{center}\Huge Stephanie Dam  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Daniel Liang  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Vivian Hew  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Olicia Choy  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Robin Chud Chen  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Melanie Pang  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Daniel Liang,  \\Welcome to SYNCS Camp! Your target is \color{red} Vivian Hew\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Stephanie Dam,  \\Welcome to SYNCS Camp! Your target is \color{red} Daniel Liang\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Olicia Choy,  \\Welcome to SYNCS Camp! Your target is \color{red} Robin Chud Chen\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Vivian Hew,  \\Welcome to SYNCS Camp! Your target is \color{red} Olicia Choy\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Melanie Pang,  \\Welcome to SYNCS Camp! Your target is \color{red} Xiyuan Hu\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Robin Chud Chen,  \\Welcome to SYNCS Camp! Your target is \color{red} Melanie Pang\end{center}\end{frame}\begin{frame}\begin{center}\Huge Xiyuan Hu  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Kerris Yap  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Ziheng Qin  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Yujin Chen  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Angelina Xu  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Edward Hwang  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Kerris Yap,  \\Welcome to SYNCS Camp! Your target is \color{red} Ziheng Qin\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Xiyuan Hu,  \\Welcome to SYNCS Camp! Your target is \color{red} Kerris Yap\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Yujin Chen,  \\Welcome to SYNCS Camp! Your target is \color{red} Angelina Xu\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Ziheng Qin,  \\Welcome to SYNCS Camp! Your target is \color{red} Yujin Chen\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Edward Hwang,  \\Welcome to SYNCS Camp! Your target is \color{red} Richard Tam\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Angelina Xu,  \\Welcome to SYNCS Camp! Your target is \color{red} Edward Hwang\end{center}\end{frame}\begin{frame}\begin{center}\Huge Richard Tam  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Rebecca Liang  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Daniel Shi  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Alex Francia  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Julia Nie  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Justin He  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Rebecca Liang,  \\Welcome to SYNCS Camp! Your target is \color{red} Daniel Shi\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Richard Tam,  \\Welcome to SYNCS Camp! Your target is \color{red} Rebecca Liang\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Alex Francia,  \\Welcome to SYNCS Camp! Your target is \color{red} Julia Nie\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Daniel Shi,  \\Welcome to SYNCS Camp! Your target is \color{red} Alex Francia\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Justin He,  \\Welcome to SYNCS Camp! Your target is \color{red} Jessy Su\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Julia Nie,  \\Welcome to SYNCS Camp! Your target is \color{red} Justin He\end{center}\end{frame}\begin{frame}\begin{center}\Huge Jessy Su  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Zeba Zaman  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge jingru ren  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Daniel Wu  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Shaun Breedon  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Tim Wang  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Zeba Zaman,  \\Welcome to SYNCS Camp! Your target is \color{red} jingru ren\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Jessy Su,  \\Welcome to SYNCS Camp! Your target is \color{red} Zeba Zaman\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Daniel Wu,  \\Welcome to SYNCS Camp! Your target is \color{red} Shaun Breedon\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi jingru ren,  \\Welcome to SYNCS Camp! Your target is \color{red} Daniel Wu\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Tim Wang,  \\Welcome to SYNCS Camp! Your target is \color{red} David Lu\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Shaun Breedon,  \\Welcome to SYNCS Camp! Your target is \color{red} Tim Wang\end{center}\end{frame}\begin{frame}\begin{center}\Huge David Lu  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Fred Yune  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Pratik Nanda  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Angela Deng  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Chloe Tran  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Daniel Oh  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Fred Yune,  \\Welcome to SYNCS Camp! Your target is \color{red} Pratik Nanda\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi David Lu,  \\Welcome to SYNCS Camp! Your target is \color{red} Fred Yune\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Angela Deng,  \\Welcome to SYNCS Camp! Your target is \color{red} Chloe Tran\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Pratik Nanda,  \\Welcome to SYNCS Camp! Your target is \color{red} Angela Deng\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Daniel Oh,  \\Welcome to SYNCS Camp! Your target is \color{red} Owen Fung\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Chloe Tran,  \\Welcome to SYNCS Camp! Your target is \color{red} Daniel Oh\end{center}\end{frame}\begin{frame}\begin{center}\Huge Owen Fung  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Tony Guan  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Grace Chen  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Nat Goria  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge SUNMO AN  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Ko Ueno  \\\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Tony Guan,  \\Welcome to SYNCS Camp! Your target is \color{red} Grace Chen\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Owen Fung,  \\Welcome to SYNCS Camp! Your target is \color{red} Tony Guan\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Nat Goria,  \\Welcome to SYNCS Camp! Your target is \color{red} SUNMO AN\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Grace Chen,  \\Welcome to SYNCS Camp! Your target is \color{red} Nat Goria\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Ko Ueno,  \\Welcome to SYNCS Camp! Your target is \color{red} Hanna Yoo\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi SUNMO AN,  \\Welcome to SYNCS Camp! Your target is \color{red} Ko Ueno\end{center}\end{frame}\newpage\begin{frame}\begin{center}\Huge Hanna Yoo  \\\end{center}\end{frame}\newpage\begin{frame}\begin{center}\Huge Hi Hanna Yoo,  \\Welcome to SYNCS Camp! Your target is \color{red} Dylan Tazawa-Lim\end{center}\end{frame}\begin{frame}\begin{center}\Huge Hi Ko Ueno,  \\Welcome to SYNCS Camp! Your target is \color{red} Hanna Yoo\end{center}\end{frame}\end{document}